An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-21 neurips-19/poly-embed.tex
meeting comments
Started clearing out Appendix

%% Jessie commented out 1/31/19 because of the updated proof to the trim TFAE, these are now no longer necessary.
%%\section{Considering unlabeled properties}
%%  Note that when $\Gamma$ is elicitable, there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
%%  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
%%  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
%%
%%  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
%%
%%
%%\begin{lemma}\label{lem:trim-subsets-not-full-dimensional}
%%Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
%%For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
%%\end{lemma}
%%\begin{proof}
%%  If there is a full-dimensional level set $\Gamma_u \subsetneq \Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for all $p \in \Gamma_u$.
%%%  (This is true because $\phi^{-1}(u) \neq \phi^{-1}(w)$ as the level sets are not equal.)
%%  However, closed, convex, full-dimensional level sets have positive Lebesgue measure in $\reals^{n-1}$,\jessiet{I don't know if we need a citation/proof for this assertion...} and thus contradicts the convexity of $G$, as convex functions are differentiable at all but a countable set of points.
%%  This in turn contradicts the elicitability of $\Gamma$, and so, we conclude that $\Gamma_u$ is not full-dimensional.
%%\end{proof}
%%
%%\begin{lemma}\label{lem:unique-opt-on-inter}
%%  Let $\Gamma:\simplex \toto \R'$ be an elicitable property such that $\trim(\Gamma)$ is finite.
%%  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
%%\end{lemma}
%%\begin{proof}
%%\jessiet{Come back and formalize}
%%  We'll use the relationship between non-redundant properties and subgradients of the expected score $G$.
%%  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
%%  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
%%  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
%%  \bigskip
%%  \jessie{Formalization below}
%%  \hrule
%%  Consider that $\trim(\Gamma)$ is non-redundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior. \jessiet{Sanity check here?}
%%  Since $\Gamma$ is elicitable, the score $G$ must be convex.
%%  For $w \in \R'$, if $\Gamma_w \subseteq \Gamma_u$, then we contradict the nonredundancy of $\trim(\Gamma)$, so we only worry about the case where $\Gamma_w \not \subseteq \Gamma_u$..
%%
%%  Suppose there is such a level set.
%%  There must be another level set $v$ so that $\Gamma_w \cap \inter{\Gamma_v}$ is nonempty, since level sets of elicitable properties are closed.
%%  Therefore, for $q \in \Gamma_w$, we observe $\Gamma(q) \subseteq \{u,w\}$ or $\{v,w\}$.
%%  More importantly- for $q \in \Gamma_w$, $\Gamma(q)$ is not constant.
%%
%%  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $q' \in \Gamma_w \cap \inter{\Gamma_v}$.
%%  Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
%%  Since there is a bijection from $\Gamma(p)$ to $\partial_p G(p)$, we then note that $|\partial_pG(p)| > 1$ on an uncountable set, and $\partial_p G(p)$ is not constant on $\conv(\{q,q'\})$.
%%  This contradicts the convexity of $G$, and in turn, the elicitability of $\Gamma$ and $\trim(\Gamma)$.
%%
%%  Therefore, for all $p \in \inter{\Gamma_u}$, we must observe $\Gamma(p) = \{u\}$.
%%
%%\end{proof}
%%
%%\begin{corollary}\label{cor:cant-span-interiors}
%%  If $\Gamma:\simplex \toto \R'$ is a non-redundant, finite elicitable property, no level set spans the interior of two other level sets.
%%  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
%%\end{corollary}
%%\jessiet{I can write something for a proof of this if you want, but it follows from the previous statement pretty quickly.}
%%
%%\begin{lemma}\label{lem:trim-full-dim}
%%  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many full-dimensional level sets.
%%  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.
%%\end{lemma}
%%\begin{proof}
%%  Consider an arbitrary level set $\theta$.
%%  If $\theta$ is not full-dimensional, we want to show that it must be the intersection of some full-dimensional level sets in $\trim(\Gamma)$.\jessiet{Why?  Add more details about why the level set can't span two full-dimensional level sets}
%%  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
%%
%%  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
%%  It must then span the interior multiple level sets, as level sets of elicitable properties are closed.
%%  By Corollary~\ref{cor:cant-span-interiors}, we contradict the elicitability of $\Gamma$.
%%  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$.
%%  As trimming a property removes such redundant reports, we then observe that $\theta \not \in \trim(\Gamma)$.
%%  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
%%\end{proof}

%\begin{lemma}\label{lem:finite-nonred-fdls}
%Let $\Gamma:\simplex \toto \R'$ be a non-redundant, finite elicitable property.
%Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
%\end{lemma}
%\begin{proof}
%Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
%Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
%Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.

%Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$.
%Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.

%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two non-redundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
%By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
%However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
%However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.

%Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
%\jessie{.... other argument}

%Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level set.s

%\end{proof}
\newpage
\section{To Sort}
\jessiet{Lol we should probably change the name of this}
\raft{No kidding!  Was this really in the COLT submission??  Hilarious.}
Several definitions from \citet{aurenhammer1987power}.
\begin{definition}\label{def:cell-complex}
  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
\end{definition}

@@

\begin{theorem}[\cite{aurenhammer1987power}]\label{thm:aurenhammer}
  A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
\end{theorem}

@@

\begin{lemma}\label{lem:polyhedral-pd-same}
  Let $f_1,\ldots,f_k:\reals^d\to\reals$ be polyhedral convex functions.
  \jessiet{Replace $k$ with $m$?}
  The power diagram induced by $\sum_{i=1}^k p_i f_i$ is the same for all $p \in \inter\simplex$.
\end{lemma}
\begin{proof}
  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.

  Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
  By \raf{Rockafellar}\jessiet{\cite{rockafellar1997convex}}, $f,f'$ are polyhedral.
  We now show that $f$ is differentiable whenever $f'$ is differentiable:
  \begin{align*}
    \partial f(x) = \{d\}
    &\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
    &\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
    &\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
    &\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
    &\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
  \end{align*}
  From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
  Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
  Thus, the power diagrams induced by $f$ and $f'$ are the same.
  The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
\end{proof}

\jessie{Original statement here:}
\begin{theorem}\label{thm:polyhedral-embed}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}

@@

\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
  \raf{Now trim is finite because the powerset of $\U$ is finite}

@@

\section{Dimension 1}\label{app:dimension-1}
\begin{proof}[Proof of Proposition~\ref{prop:embed-trim}]
  Let $L$ elicit $\Gamma$.

@@

\begin{definition}\label{def:monotone-prop}
  A property $\Gamma:\simplex\toto\R$ is \emph{monotone} if there are maps $a:\R\to\reals^\Y$, $b:\R\to\reals^\Y$ and a total ordering $<$ of $\R$ such that the following two conditions hold.
  \begin{enumerate}
  \item For all $r\in\R$, we have $\Gamma_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
  \item For all $r < r'$, we have $a(r) \leq b(r) \leq a(r') \leq b(r')$ (component-wise).
  % \item For all $r,r'\in\R$ and $p\in\Gamma_{r'}\setminus\Gamma_r$, we have $b(r) \cdot p < 0 \implies r' > r$ and $a(r) \cdot p > 0 \implies r' < r$.
  \end{enumerate}
\end{definition}

\begin{proof}[Proof of Proposition~\ref{prop:orderable-embed}]
  Let $\R = \{r_1,\ldots,r_k\}$ be the report space for $\gamma$.
  From Lemma~\ref{lem:prop-L-monotone}, stating that finite properties are orderable if and only if they are monotone, we have functions $a:\R\to\reals^\Y, b:\R\to\reals^\Y$ satisfying the following: (i) $\gamma_{r_i} = \{p\in\simplex : \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$ for all $i\in\{1,\ldots,k\}$, and (ii) $a(r_i) \leq b(r_i) = a(r_{i+1}) \leq b(r_{i+1})$ for all $i \in \{1,\ldots,k-1\}$.
  We now define $\varphi(r_i) = i \in \reals$, and define $L$ as follows:
  \begin{equation*}
    L(u)_y =
    \begin{cases}
      a(r_1) u & u < 1 \\
      c_i + b(r_i) u & u \in [i,i+1), i\in\{1,\ldots,k\} \\
      c_k + b(r_k) u & u \geq k+1
    \end{cases}~,
  \end{equation*}
  where the $c_i$ are chosen to make $L(u)_y$ continuous, namely, $c_i = \sum_{j=1}^{i} a(r_j)_y$.
  (Recall that $b(r_i) = a(r_{i+1})$.)
  By the condition (ii) above, $L(\cdot)_y$ is convex for all $y\in\Y$, and moreover, its subgradients at $\varphi(\R) = \{1,\ldots,k\}$ are given by
  $\partial L(i)_y = [a(r_i)_y,b(r_i)_y]$.
  \jessiet{I believe it, but it might help a reader to explain why it's convex a little more.}
  By condition (i), for all $i\in\{1,\ldots,k\}$ and $p\in\simplex$ we now have
  \begin{align*}
    i \in \prop{L}(p)
    &\iff 0 \in \partial \inprod{p}{L(i)} \\
    % &\iff 0 \in \sum_{y\in\Y} p_y \partial L(i)_y \\
    &\iff 0 \in \sum_{y\in\Y} p_y [a(r_i)_y,b(r_i)_y] \\
    &\iff \inprod{a(r_i)}{p} \leq 0 \leq \inprod{b(r_i)}{p} \\
    &\iff r_i \in \gamma(p)~,
  \end{align*}
  where the sum is a Minkowski sum.
\end{proof}

\begin{lemma}\label{lem:orderable-monotone}
  A finite property is orderable if and only if it is monotone.
\end{lemma}
\begin{proof}
  Let $\gamma:\simplex\toto\R$ be finite and monotone.
  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.

  For the converse, let $\gamma:\simplex\toto\R$ be finite and orderable.
  From~\cite[Theorem 4]{lambert2018elicitation}, we have positively-oriented normals $v_i\in\reals^\Y$ for all $i \in \{1,\ldots,k-1\}$ such that $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v_i}{p} = 0\}$, and moreover, for all $i \in \{2,\ldots,k-1\}$, we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v_{i-1}}{p} \leq 0 \leq \inprod{v_i}{p}\}$, while $\gamma_{r_1} = \{p\in\simplex : 0 \leq \inprod{v_1}{p} \}$ and $\gamma_{r_k} = \{p\in\simplex : \inprod{v_{k-1}}{p} \leq 0\}$.
  \jessiet{Should the sign on $\gamma_{r_k}$ be changed?}
  From the positive orientation of the $v_i$, we have for all $p\in\simplex$ that $\sgn(\inprod{v_i}{p})$ is monotone in $i$.
  In particular, it must be that for all $y$, $\sgn((v_i)_y)$ is monotone in $i$, taking the distribution with all weight on outcome $y$.
  % (Similarly, if $\gamma(\ones_y) = \{r_j,r_{j+1}\}$, then $(v_i)_y = v_i \cdot \ones_y < 0$ for $i < j$, $(v_j)_y = 0$, and $(v_i)_y > 0$ for $i > j$.)
  \raft{This observation could use a better proof.}

  For all $i\in\{2,\ldots,k-1\}$, we wish to find $\alpha_i \geq 0$ such that $v_{i-1} \leq \alpha_i v_i$ (component-wise).
  \jessiet{How should $w$ be interpreted?}
  To this end, fix $i$ and let $v = v_{i-1}, w = v_{i}, \alpha=\alpha_i$.
  By the above, there is no $y\in\Y$ with $v_y > 0 > w_y$, so the condition $v \leq \alpha w$ is equivalent to the following:

  \begin{enumerate}
  \item[(i)] For all $y$ with $v_y,w_y < 0$, $\alpha \leq v_y/w_y$.
  \item[(ii)] For all $y$ with $v_y,w_y > 0$, $\alpha \geq v_y/w_y$.
  \end{enumerate}
  Defining $\Y^- = \{y\in\Y: v_i,w_y < 0\}, \Y^+ = \{y\in\Y: v_i,w_y > 0\}$, these conditions are in turn equivalent to $\min_{y\in\Y^-} v_y/w_y \geq \max_{y\in\Y^+} v_y/w_y$, with the usual conventions $\min \emptyset = \infty,\; \max \emptyset = -\infty$.
  Suppose this inequality were not satisfied.
  Then we would have $y \in \Y^-,y'\in\Y^+$ such that $0 < v_y/w_y < w_{y'}/v_y$, which would in turn imply $|v_y|/v_{y'} < |w_y| / w_{y'}$.
  Letting $c = \tfrac 1 2 \left(|w_y| / w_{y'} + |v_y|/v_{y'}\right)$ and taking $p$ to be the distribution with weight $1/(1+c)$ on $y$ and $c/(1+c)$ on $y'$, we see that
  \begin{align*}
    \inprod{v}{p} &= \frac 1 {1+c} \left(v_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) > \frac 1 {1+c} \left(v_y + (|v_y|/v_{y'})v_{y'}\right) = 0
    \\
    \inprod{w}{p} &= \frac 1 {1+c} \left(w_y + \tfrac 1 2 (|w_y| / w_{y'} + |v_y|/v_{y'})v_{y'}\right) < \frac 1 {1+c} \left(w_y + (|w_y|/w_{y'})w_{y'}\right) = 0~,
  \end{align*}
  thus violating the observation that $\sgn(\inprod{v_i}{p})$ is monotone in $i$ (recall that $v = v_{i-1}, w = v_{i}$).

  We can now construct the $a,b$ in Definition~\ref{def:monotone-prop}.
  Letting
  \[\alpha_i = \tfrac 1 2 \left(\min_{y\in\Y^-(i)} (v_{i-1})_y/(v_{i})_y + \max_{y\in\Y^+(i)} (v_{i-1})_y/(v_{i})_y\right)~,\] the preceding argument shows that $v_{i-1} \leq \alpha_i v_{i}$ for all $i \in \{2,\ldots,k-1\}$.
  We now set $b(r_i) = a(r_{i+1}) = (\prod_{j=2}^i \alpha_j) v_i$ for $i\in\{1,\ldots,k-1\}$, as well as $a(r_1) = -\max_{y\in\Y} |(v_1)_y|\ones$ and $b(r_k) = \max_{y\in\Y} |a(r_k)_y|\ones$, where $\ones\in\reals^\Y$ denotes the all-ones vector.

  The above establishes the second condition of monotone properties in Definition~\ref{def:monotone-prop}.
  To see the first condition, note that we have already established it for $i\in\{2,\ldots,k-1\}$.
  For $i=1,k$, we merely observe that $\inprod{a(r_1)}{p} \leq 0$ and $\inprod{b(r_k)}{p} \geq 0$ for all $p\in\simplex$.
\end{proof}

@@

We now prove the remaining results.
%Proposition~\ref{prop:indirect-orderable}, which states the following: if convex $L : \reals \to \reals^\Y$ indirectly elicits a finite elicitable property $\gamma$, then $\gamma$ is orderable.
\begin{proof}[of Proposition~\ref{prop:indirect-orderable}]
  Let $\gamma:\simplex\toto\R$.
  From Lemma~\ref{lem:prop-L-monotone}, $\Gamma := \prop{L}$ is monotone.
  Let $\psi:\reals\to\R$ be the calibrated link from $\Gamma$ to $\gamma$.
  From Lemma~\ref{lem:pbar}, we have $\Pbar_r = \gamma_r$ for all $r\in\R$, where $\Pbar_r$ is the closure of the convex hull of $\bigcup_{u\in\psi^{-1}(r)} \Gamma_u$.

  As $\Gamma$ is monotone, we must have $a,b : \R\to\reals^\Y$ such that $\Pbar_r = \{p\in\simplex : \inprod{a(r)}{p} \leq 0 \leq \inprod{b(r)}{p} \}$.
  (Take $a(r)_y = \inf_{u\in\psi^{-1}(r)} a(u)_y$ and $b(r)_y = \sup_{u\in\psi^{-1}(r)} b(u)_y$.)
  Now taking $p_r\in\inter\gamma_r$ and picking $u_r \in \Gamma(p_r)$, we order $\R = \{r_1,\ldots,r_k\}$ so that $u_{r_i} < u_{r_{i+1}}$ for all $i\in\{1,\ldots,k-1\}$.
  (The $u_{r_i}$ must all be distinct, as we chose $p_r$ so that $\gamma(p_r) = \{r\}$, so $\psi(u_{r_i}) = r_i$ for all $i$.)

  Let $i\in\{1,\ldots,k-1\}$.
  By monotonicity of $\Gamma$, we must have $a(r_i) \leq b(r_i) \leq a(r_{i+1}) \leq b(r_{i+1})$.
  As $\bigcup_{r\in\R} \Pbar_r = \bigcup_{r\in\R} \gamma_r = \simplex$, we must therefore have $b(r_i) = a(r_{i+1})$.
  Finally, we conclude $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{b(r_i)}{p} = 0\}$.
  As these statements hold for all $i\in\{1,\ldots,k-1\}$, $\gamma$ is orderable.
\end{proof}

\newcommand{\floor}[1]{\lfloor #1\rfloor}
\begin{proof}[of Theorem~\ref{thm:1d-tfae}]
  As remarked before the theorem statement, it remains only to show $1 \iff 5$.
  \raft{This got a tad hand-wavy toward the end, but I think it's not too bad.}
  For the forward direction, by Lemma~\ref{lem:orderable-monotone}, we have $v(0),\ldots,v(k)\in\reals^\Y$ such that the coefficients $v(i)_y$ are monotone in $i$ for all $y\in\Y$, and the following two conditions hold: (1) \jessiet{Change to (i) and (ii) for consistency?} for all $i\in\{1,\ldots,k\}$ we have $\gamma_{r_i} = \{p\in\simplex : \inprod{v(i-1)}{p} \leq 0 \leq \inprod{v(i)}{p} \}$, and (2) for all $i\in\{1,\ldots,k-1\}$ we have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{v(i)}{p} = 0\}$.
  Letting $\floor{u}$ denote the floor function, and $\mathrm{mod}(u) := u - \floor{u}$, we extend the above definition to $v:[0,k]\to\reals^\Y$ given by
  \begin{align*}
    v(u) = (1-\mathrm{mod}(u))v(\floor{u}) + \mathrm{mod}(u)v(\floor{u}+1)~,
  \end{align*}
  which is continuous by construction.
  Moreover, $v(\cdot)_y$ is monotone for all $y\in\Y$.
  As the level sets $\gamma_r$ are full-dimensional (Lemma~\ref{lem:finite-full-dim}), for all $p\in\simplex$, there is a unique $u\in[0,k]$ such that $\inprod{v(u)}{p} = 0$.
  \jessiet{Why is the above statement true on boundaries of level sets?}
  We conclude that the property $\Gamma:\simplex\to[0,k]$ given by $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$ is a single-valued property, which continuous as $v$ is continuous.
  Finally, the link $\psi(u) = \floor{u}+1$ is calibrated from $\Gamma$ to $\gamma$.

  For the converse, let $\Gamma:\simplex\to\reals$ be a continuous, non-locally-constant, elicitable property, with a calibrated link $\psi:\reals\to\R$ to $\gamma$.
  By~\cite{lambert2018elicitation,steinwart2014elicitation}, we have some continuous $v:\Gamma(\simplex)\to\reals^\Y$ such that for all $u\in\Gamma(\simplex)$ we have $\Gamma_u = \{p\in\simplex : \inprod{v(u)}{p} = 0\}$.

  Let $c_r = \inf\psi^{-1}(r)$ and $d_r = \sup \psi^{-1}(r)$ for all $r\in\R$, and let $I_r = (c_r,d_r)$.
  By continuity, $\Gamma^{-1}(I_r)$ is an open set, and the definition of calibration, we have $\Gamma^{-1}(I_r) \subseteq \gamma_r$; we conclude $\Gamma^{-1}(I_r) \subseteq \inter\gamma_r$. \jessiet{Why $\subseteq$ and not $=$?}
  Again by continuity of $\Gamma$, we must have $\Gamma(\gamma_r) = [c_r,d_r] := \overline I_r$.

  As the interiors of the level sets of $\gamma$ are disjoint (Theorem~\ref{thm:aurenhammer}), the intervals $\{I_r:r\in\R\}$ must also be disjoint.
  Define an ordering $\R = \{r_1,\ldots,r_k\}$ so that $I_{r_1} < \cdots < I_{r_k}$.
  Then for all $i\in\{1,\ldots,k-1\}$ we must have $d_{r_i} = c_{r_{i+1}}$; otherwise, the point $u = \tfrac 1 2 (d_{r_i} + c_{r_{i+1}})$ would not belong to any $\overline I_r$, and as $\Gamma(\simplex) = \Gamma(\bigcup_r\gamma_r) = \bigcup_r \overline I_r$, this would violate continuity of $\Gamma$.
  We conclude that $\gamma_{r_i}\cap\gamma_{r_{i+1}} = \Gamma_{d_i} = \{p\in\simplex : \inprod{v(d_i)}{p} = 0\}$ for all $i\in\{1,\ldots,k-1\}$.
\end{proof}

>>>>

\newpage
\section{Power diagrams}
First, we present several definitions from Aurenhammer~\cite{aurenhammer1987power}.
\begin{definition}\label{def:cell-complex}
  A \emph{cell complex} in $\reals^d$ is a set $C$ of faces (of dimension $0,\ldots,d$) which (i) union to $\reals^d$, (ii) have pairwise disjoint relative interiors, and (iii) any nonempty intersection of faces $F,F'$ in $C$ is a face of $F$ and $F'$ and an element of $C$.
\end{definition}

@@

\begin{theorem}[Aurenhammer~\cite{aurenhammer1987power}]\label{thm:aurenhammer}
  A cell complex is affinely equivalent to a convex polyhedron if and only if it is a power diagram.
\end{theorem}

@@

\begin{lemma}\label{lem:polyhedral-pd-same}
  Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
  The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
\end{lemma}
\begin{proof}
  For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
  Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
  It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
  Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.

  Now let $f := \sum_{i=1}^k f_i$ with epigraph $P$, and $f' := \sum_{i=1}^k p_i f_i$ with epigraph $P'$.
  By Rockafellar~\cite{rockafellar1997convex}, $f,f'$ are polyhedral.
  We now show that $f$ is differentiable whenever $f'$ is differentiable:
  \begin{align*}
    \partial f(x) = \{d\}
    &\iff \sum_{i=1}^k \partial f_i(x) = \{d\} \\
    &\iff \forall i\in\{1,\ldots,k\}, \; \partial f_i(x) = \{d_i\} \\
    &\iff \forall i\in\{1,\ldots,k\}, \; \partial p_i f_i(x) = \{p_id_i\} \\
    &\iff \sum_{i=1}^k \partial p_if_i(x) = \left\{\sum_{i=1}^k p_id_i\right\} \\
    &\iff \partial f'(x) = \left\{\sum_{i=1}^k p_id_i\right\}~.
  \end{align*}
  From the above observations, every facet of $P$ is determined by the derivative of $f$ at any point in the interior of its projection, and vice versa.
  Letting $x$ be such a point in the interior, we now see that the facet of $P'$ containing $(x,f'(x))$ has the same projection, namely $\{x'\in\reals^d : \nabla f(x) \in \partial f(x')\} = \{x'\in\reals^d : \nabla f'(x) \in \partial f'(x')\}$.
  Thus, the power diagrams induced by $f$ and $f'$ are the same.
  The conclusion follows from the observation that the above held for any strictly positive weights $p$, and $f$ was fixed.
\end{proof}

@@

\jessie{Original statement here:}
\begin{theorem}\label{thm:polyhedral-embed}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a non-redundant elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
  \raf{Now trim is finite because the powerset of $\U$ is finite}

@@

\section{Embedding properties}\label{app:embed-props}
\begin{proof}[Proof of Proposition~\ref{prop:embed-trim}]
  Let $L$ elicit $\Gamma$.

@@

@@
